The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Resolve a todo.

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{python_mesh.png}
\caption{\it The mesh generated by the Python code shown in the main
  text. Cells are colored by material id.}
\label{fig:pymesh}
\end{figure}

@@

All triangulations created from within Python are serial. However,
once the mesh is designed, the triangulation can be serialized along
with the auxiliary information about possible refinement, boundaries,
materials and manifolds. This object can be easily deserialized within
a C++ program for subsequent production runs. Furthermore, such a
serialized triangulation can also be used in the construction of
\texttt{parallel::shared}, \texttt{parallel::disrtibuted}, and
\texttt{parallel::fullydistributed} triangulations (see also Section~\ref{subsec:pft}).

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item Two functions that provide information about all processes,
  namely
  \begin{itemize}
 \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
 \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
  \end{itemize}
have been deprecated. As discussed in
Subsection~\ref{subsec:performance}, deal.II by default no longer
stores information for all processes on all processes, but only
local or locally-relevant information. On the other
hand, if necessary, global information can still be computed using,
for example, calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item
  \todo[inline]{What else is worth mentioning? Someone needs to go
    through the list of incompatible changes...}
\end{itemize}

>>>>

\usepackage{floatflt}

@@

@@

\begin{floatingfigure}[r]{0.3\textwidth}
  \centering
  \vspace*{-1.4cm}
  \includegraphics[width=0.3\textwidth]{python_mesh.png}
  \vspace*{-5mm}
  \caption{\it The mesh generated by the Python code shown in the main
    text. Cells are colored by material id.}
  \vspace*{0.2cm}
\label{fig:pymesh}
\end{floatingfigure}
All triangulations created from within Python are serial. However,
once the mesh is designed, the triangulation can be serialized along
with the auxiliary information about possible refinement, boundaries,
materials and manifolds. This object can be easily deserialized within
a C++ program for subsequent production runs. Furthermore, such a
serialized triangulation can also be used in the construction of
\texttt{parallel::shared}, \texttt{parallel::disrtibuted}, and
\texttt{parallel::fullydistributed} triangulations (see also Section~\ref{subsec:pft}).

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
\item Two functions that provide information about all processes,
  namely
  \begin{itemize}
 \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
 \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
  \end{itemize}
have been deprecated. As discussed in
Subsection~\ref{subsec:performance}, deal.II by default no longer
stores information for all processes on all processes, but only
local or locally-relevant information. On the other
hand, if necessary, global information can still be computed using,
for example, calling
\texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.

\item A corresponding change has been made in parallel triangulation
  classes:
  \texttt{parallel::} \texttt{TriangulationBase::compute\_n\_locally\_owned\_active\_cells\_per\_processor()}
  can be used to obtain information about how many cells each
  process owns.
\end{itemize}
